Astro 507; Problem Set 4

### 2022-03-09 pset4/solutions.tex
pset4 q3c
pset4 q3d+e

\question{3c. \textbf{Evaluate mass}}
\answer{

}

\question{3d. \textbf{Polytropes}}
\answer{

}

\question{3e. \textbf{Lane-Emden equation}}
\answer{

}

>>>>

\question{3c. \textbf{Evaluate mass}}
\answer{
    Plugging these numbers in we find that the lower limit corresponds to
    \begin{equation}
        \boxed{ M_{\rm rad} > 29.2 \unit{M_{\odot}} }
    \end{equation}
    which is fairly close to what we would expect for radiation-dominated stars, how festive!
}

\pagebreak

\question{3d. \textbf{Polytropes}}
\answer{
    If we assume that all of the pressure in the star comes from radiation pressure then, from hydrostatic equilibrium, we have that
    \begin{align}
        \frac{P}{R} &\approx \frac{G M^2}{R^5} \\
        P &\approx G M^2 \qty(\frac{M}{\rho})^{-4/3} \\
        \implies P &\propto \rho^{4/3}
    \end{align}
    Therefore we find that $\Gamma = 4/3$ in this case and so the polytrope index is $n = 3$, like a relativistic gas, which I think makes sense for radiation-dominated stars! I \textit{think} the assumption we made that results in the pressure just being a function of density and not temperature is just that we are in hydrostatic equilibrium and that all of the pressure comes from radiation but I'm honestly not sure.
}

\question{3e. \textbf{Lane-Emden equation}}
\answer{
    If we could make these assumptions then we could use the Lane-Emden Equation in the same way as in lecture, specifically with $n = 3$. This would give us the density of the star as a function of the radius like in the plot in lecture 11 slide 20 and so we'd know the interal structure of stars above the radiation-dominated mass limit.
    \todo{need to check with Eric what he actually wants from us on this one}
}
